\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}

\hypersetup{
	linktoc=all,
	hidelinks,
}

\begin{document}
	\thispagestyle{empty}
	\tableofcontents
	
	\newpage
	\setcounter{page}{1}
	\section{The end of behaviorism}
	Behaviorism was the leading school of psychology in the 19th century. Psychology is a difficult subject to study as it deals with very delicate and subjective topics such as consciousness and emotions which can only be felt by oneself.\\
	Behaviorism restricts psychology to only observable objective phenomena such as behavior in order to make psychology a true science.
	\subsection{Classical conditioning}
	Reflexes are behaviors that are mediated by the central nervous system such as the knee-jerk reflex or the startle response. Reflexes are very fast and automatic.\\
	Reflexes can be dampened (habituated) through repeated exposure.
	\subsection{Pavlov}
	Pavlov was conducting research about the different types of saliva that dogs produce with different foods.\\
	The research assistants noticed that the dogs began to salivate before even being given the food, Pavlov found this phenomena so interesting he switched his research objective to uncover the reason behind the early salivation.\\
	Pavlov began ringing a bell before giving them food, later he rang the bell without food and the dogs still salivated.\\
	Neutral stimulus has no effect or connection to the result.\\
	Unconditional stimulus has an unconditional response.\\
	By pairing neutral stimulus with unconditional stimulus you can produce a conditioned response.\\
	Discrimination training is done by only giving the unconditional stimulus with a specific neutral stimulus and not other neutral stimuli.\\
	If you don't give discrimination training during conditioning then you're giving generalization training, where any range of neutral stimuli gives a conditioned response.
	
	\newpage
	\section{Mechanics of conditioning}
	We can look at classical conditioning with a different point of view. By associating the sound of bell with the image of food, and that the imagination of food made the dog expect food which makes the dogs salivate.\\
	Cognitivisim is about a stimulus-stimulus connection instead of a stimulus-response connection suggested by behaviorism.\\
	Rats display a natural freezing response to loud noises, after conditioning the rats to expect loud sounds after pairing them with a light they began displaying a freezing to the lights. Later the scientist habituated half the rats to the loud sound until they no longer produced the freezing response.\\
	The result was as cognitivist expected, that the stimuli of light and sound were connected and habituating one habituates the other. This is unlike what the behaviorists expected, that the stimulus-reaction connection between light and freezing.
	
	\section{Operant conditioning}
	Also called reinforcement learning. It works with self-initiating behavior that is either rewarded or punished.\\
	Behavior that produces a satisfying effect is called operant responses.\\
	The famous experiment for operant conditioning is the Skinner Box, in which rats were put in boxes where if they pull the correct lever they get food, while the wrong lever gives electric shock.\\
	Shaping is a technique to teach creatures sequences of actions by rewarding successive steps in complex behavior.\\
	Continuous reinforcement is always giving the reinforcer after a desired response is given. Partial reinforcement is giving the reinforcer after a certain number or interval of desired responses.\\
	Different partial reinforcement methods have different extinction rates.
	
	\section{Cognition and computation}
	If something can compute any computable function, we call it Turing complete.\\
	The just noticeable difference is the minimal difference between two stimuli at which the difference is detected. There is a formula for this relation.\\
	Early selection models are where the input is filtered early on in the cognitive process, it is not completely correct.
\end{document}
